### 2015-11-20 section/2_workless.tex
address linhai's comments

\section{\Tool design}
\label{sec:design}
\Tool consists of a series of analysis that
judges whether a given loop belongs to any root cause type discussed in
Section \ref{sec:study_tax}.
Its design
follows the following principles.
\begin{itemize}
\item Failure diagnosis, not bug detection. \Tool will be  
used together with other performance diagnosis tools \cite{SongOOPSLA2014}
and focus on a small
number of loops that are most correlated with a specific performance symptom,
instead of being applied to the whole program. Therefore, we will have different
design trade-offs in terms of coverage and accuracy, comparing with 
bug detection tools.

@@

>>>>

\section{\Tool design}
\label{sec:design}
\Tool consists of a series of analysis that
judges whether a given loop belongs to any root-cause type discussed in
Section \ref{sec:study_tax}.
Its design
follows the following principles.
\begin{itemize}
\item Failure diagnosis, not bug detection. \Tool will be  
used together with other performance diagnosis tools \cite{SongOOPSLA2014}
and focus on a small
number of loops that are most correlated with a specific performance symptom,
instead of being applied to the whole program. Therefore, we will have different
design trade-offs in terms of coverage and accuracy, comparing with 
bug detection tools.

@@

\paragraph{Usage scenario}
Existing profilers and statistical debugging tool can
identify suspicious loops that are most correlated with 
certain performance 
symptoms \cite{SongOOPSLA2014}. 
\Tool will analyze
these suspicious loops, identify which loop(s) is inefficient, why it is
inefficient, and provide fix suggestions. This analysis could be
conducted during in-house diagnosis, where failure-triggering inputs
are available. It could also be conducted during production runs, with
the run-time analysis component of \Tool running 
at user sites.
